Do motif roles provide unique information about species risk of extinction?

### 2021-08-18 manuscript/motifs_vs_degree.tex

    Participation in the apparent competition motif was strongly negatively correlated with in-degree and positively correlated with trophic level --a high proportion of the apparent competition motif implies a low in-degree and high trophic level, both of which are associated with lower probabilities of persistence.
    Moreover, the relationships between persistence and in-degree and apparent competition have a similar interaction with disturbance.
    Both are associated with lower persistence at low disturbance but increased persistence at high disturbance. 
    This may occur because, when disturbance is high, connections to many prey species mean many sources of bottom-up disturbance.

@@

%The remaining two motifs are strongly related to both in-degree and trophic level and must be explained using a combination of the two simpler network properties.
%Motifs can, in this sense, act as a tool for synthesizing the information provided by multiple other measures of a species' place in its community, as well as interactions between them.
%The three-species chain motif, for example, is moderately negatively correlated with in-degree and moderately positively correlated with trophic level. 
%The relationship between persistence and the chain motif therefore combines the overall negative effect of high trophic level with the interaction between in-degree and disturbance; leading the chain motif to have little relationship to persistence at low disturbance and an increasingly negative relationship at higher disturbance.
Likewise, the three-species chain motif is correlated with trophic level, but the relationship is positive and a high proportion of this motif indicates a high trophic level. Hence, the negative effect on persistence of having a high proportion of the three-species chain motif is likely connected to the high trophic level. 
- sig. correlated with in-degree (I think???) but does not show up in the relationship to persistence
- chain has to be capturing effect of something else that acts like positive correlation with in-degree and is stronger than effect of in-degree.

@@

>>>>

    Participation in the apparent competition motif was strongly negatively correlated with in-degree and positively correlated with trophic level --a high proportion of the apparent competition motif implies a low in-degree and high trophic level, both of which are associated with lower probabilities of persistence.
    Moreover, the relationships between persistence and in-degree and apparent competition have a similar interaction with disturbance.
    Both are associated with lower persistence at low disturbance but increased persistence at high disturbance. 
    This may occur because, when disturbance is high, connections to many prey species mean many sources of bottom-up disturbance.
    - also strongly associated with trophic level but effects don't match. So there must be something else affecting the affect of apparent competition

@@

%The remaining two motifs are strongly related to both in-degree and trophic level and must be explained using a combination of the two simpler network properties.
%Motifs can, in this sense, act as a tool for synthesizing the information provided by multiple other measures of a species' place in its community, as well as interactions between them.
%The three-species chain motif, for example, is moderately negatively correlated with in-degree and moderately positively correlated with trophic level. 
%The relationship between persistence and the chain motif therefore combines the overall negative effect of high trophic level with the interaction between in-degree and disturbance; leading the chain motif to have little relationship to persistence at low disturbance and an increasingly negative relationship at higher disturbance.
Likewise, the three-species chain motif is correlated with trophic level, but the relationship is positive and a high proportion of this motif indicates a high trophic level. Hence, the negative effect on persistence of having a high proportion of the three-species chain motif is likely connected to the high trophic level. 
- sig. correlated with in-degree (I think???) but does not show up in the relationship to persistence
- something else is related to chain that acts like a positive association with in-degree that is strong enough to cancel out the negative relationship with in-degree

@@

- maybe end with a brief summary/discussion of the effect of disturbance: seem to see a "tipping point" in both degree and motifs.
